Probabilistic Programming

### 2014-04-21 paper/paper.tex
Discuss high-order model in conclusions

The autocomplete snippets are generated as follows:
\begin{enumerate}
	\item Parse the contents of the current file into an AST.
	\item Find the node path corresponding to the cursor by traversing the AST.
		%This represents the program context at which the code snippets should
		%be generated.
	\item Generate programs starting from the node path of the cursor.
	\item Present the programs to the user as code completion snippets.
\end{enumerate}

@@

%Design decisions, HCI factors

@@

This is a limitation of the current model, that identifier names are chosen
probabilistically based on their position in the code, without regard to whether
they are in scope and without refering to anything in another part of the
program. Because of this limitation, the Guided IDE is not useful for practical
purposes. We consider some alternative approaches for the Guided IDE using a
similar model.

@@

%\subsection{Limitations of the IDE}

@@

%Choosing valid identifiers, matching identifiers

Other applications of the model: genetic algorithms

@@

	\bibitem{esprima} Ariya Hidayat {\em Esprima}
		URL = \url{http://esprima.org/}

	\bibitem{markov} Takis Konstantopoulos {\em Introductory lecture notes on
		Markov Chains and Random Walks} Uppsala University,
		URL = \url{http://www2.math.uu.se/~takis/L/McRw/mcrw.pdf}

	\bibitem{escodegen} Yusuke Suzuki {\em Escodegen}
		URL = \url{https://github.com/Constellation/escodegen}

	\bibitem{parser api} Mozilla Developer Network {\em SpiderMonkey Parser API}
		URL = \url{https://developer.mozilla.org/en-US/docs/SpiderMonkey/Parser_API}

>>>>

The autocomplete snippets are generated as follows:
\begin{enumerate}
	\item Parse the contents of the current file into an AST.
	\item Find the node path corresponding to the cursor by traversing the AST.
	\item Generate programs starting from the node path of the cursor.
	\item Present the programs to the user as code completion snippets.
\end{enumerate}

@@

@@

It is a limitation of the current model that identifier names are chosen
probabilistically based on their position in the code, without regard to whether
they are in scope and without refering to anything in another part of the
program. Because of this limitation, the Guided IDE is not useful for practical
purposes. We consider some alternative approaches for the Guided IDE using a
similar model.

@@

%Other applications of the model: genetic algorithms

@@

Just as our approach of modeling a program with a tree-based Markov chain is a
higher order model than a linear Markov chain of the program source code tokens,
there may be applications of probabilistic modeling to higher-order
representations of programs than the AST, such as a higher-order abstract syntax
\cite{hosa}. Such an application may model the relationship between different
parts of an AST, and handle scoping of variables to model identifiers
abstractly.

With a more sophisticated model of identifiers that could generate programs with
identifiers in meaningful relation to eachother, Probabilistic Programming could
be used to generate semantically valid programs, for greater assistive,
expressive, and programatic power.

@@

	\bibitem{esprima} Ariya Hidayat {\em Esprima}
		\\\url{http://esprima.org/}

	\bibitem{markov} Takis Konstantopoulos {\em Introductory lecture notes on
		Markov Chains and Random Walks.} Uppsala University,
		\\\url{http://www2.math.uu.se/~takis/L/McRw/mcrw.pdf}

	\bibitem{hosa} Frank Pfenning, Conal Elliott
		{\em Higher-Order Abstract Syntax.}
		ACM SIGPLAN Notices. Vol. 23. No. 7. ACM, 1988.
		\\\url{http://www.cs.cmu.edu/~fp/papers/pldi88.pdf}

	\bibitem{escodegen} Yusuke Suzuki {\em Escodegen}
		\\\url{https://github.com/Constellation/escodegen}

	\bibitem{parser api} Mozilla Developer Network {\em SpiderMonkey Parser API}
		\\\url{https://developer.mozilla.org/en-US/docs/SpiderMonkey/Parser_API}
